%% start of file `template.tex'.
%% Copyright 2018 Kevin Dang Nguyen (khoa.kevin@gmail.com).

\documentclass[letterpaper,12pt,final]{moderncv}        

    % moderncv themes
    \moderncvtheme[burgundy]{classic}                 
    % character encoding
    \usepackage[utf8]{inputenc}
    % adjust the page margins
    \usepackage[scale=0.8]{geometry}
    \recomputelengths
    %change font
    \usepackage{lmodern}

    
    % personal data
    \name{Kevin}{Nguyen}
    \title{Product Manager}                               
    \address{1-60 Hamilton St.}{Toronto, ON}{M4M 2C8}
    \phone[mobile]{416 906 3238}
    \email{khoa.kevin@gmail.com}                               

    \begin{document}

    \maketitle

    \section{Experience}
    \cventry{2013--2018}{Product Manager}{SchoolMessenger | West Corporation}{Toronto, ON}{}{With over 1400 clients, SchoolMessenger is one of the leading k12 communications providers in North America. I manage the CMS product with additional markets in healthcare facilities and municipalities.\newline{}%
    \begin{itemize}%
    \item Lead the CMS platform that allows schools, cities and healthcare facilities to build and manage their public websites. 
        \begin{itemize}%
            \item Identified growth and cross-sale opportunities internal and external to organization leading ot a 30\% growth in 2017.
            \item 15\% increase in retention after validating bets from internal analytics with client outreach.
            \item Increased revenue per client by 8\% after introducing features to streamline implementation process.
        \end{itemize}
    \item Developed end-to-end product plan and roadmap to ensure timely and effective delivery of the application.
        \begin{itemize}
            \item Standardized the process for gathering input from the cross functional team and created a template for consistent feedback.
            \item Developed templates for writing stories and documented the bug triaging process.
        \end{itemize}
    \item Introduced SCRUM to software development life cycle and provide day-to-day coordination to the team of 13 Developers, 3 QAs and 1 Designer.
      \begin{itemize}%
        \item Facilitated SCRUM within the Scaled Agile Framework to ensure alignment across the larger organization.
        \item Successfully transitioned the team from TFS and SVN to JIRA and GIT.
      \end{itemize}
    \end{itemize}
    \vspace{5mm}
    \textbf {Product Analyst} (2013-2014) 
      \begin{itemize}
        \item Prior to being promoted to the Product Manger of the CMS, I was the Product Analyst for the CMS and its Sister Brand: Talentova.
        \item Developed the  Accessibility initiative for the product to ensure ADA standards were met to address market and legal requirements for education and government websites.
        \item Owned and delivered the Innovation Management Product. A crowd-source ideas engine to be used in closed ecosystems to generate ideas and facilitate project teams.
      \end{itemize}
    }
    \vspace{5mm}
    \cventry{2012--2013}{Technical Integration Specialist}{Manulife Financial}{Toronto}{}{This was an 8 month Co-Op work term as part of my University Degree.\newline{}
    \begin{itemize}
        \item Facilitated deployment of Windows 7 workstations.
        \item Conducted Vendor interviews to ensure user requirements are met.
        \item Developed process and tool to inventory all hardware and software in the Toronto Department of Manulife Asset Management.
        \item Create database of track the inventory in order to manage changes to each workstation.
    \end{itemize}
    }
    \vspace{5mm}
    \cventry{2011--2011}{Business Systems Analyst}{Royal Bank of Canada}{Toronto, ON}{}{This was a 4 month Co-Op work term as part of my University Degree.\newline{}
    \begin{itemize}
        \item Performed system requirements gathering to replace a suite of tools with a single vendor solution.
        \item contributed and maintained a repository of Business Process Maps.
        \item Identified redundancies and pain points in the current processes.
        \item Made recommendations to improve the future state process through Gap Analysis.
    \end{itemize}
    }
    \section{Education}
    \cventry{2008--2013}{Information Technology Management}{Ryerson University}{Toronto, ON}{}{
        \textbf{Highlights}
        \begin{itemize}
            \item Dean's List 2011-2012
            \item Partnered with Scotiabank for final year project to develop new data mining and reporting system
        \end{itemize}
        \textbf{Completed Coursework in Major includes:}
        \begin{itemize}
            \item Systems Analysis and Design (UML, OOP)
            \item Relational Database Design
            \item Information Security Engineering
            \item Business Design and Process Improvement
        \end{itemize}
    }

    \section{Tools/Technical Knowledge}
    \cvline{\textbf{Tools}}{JIRA, Confluence, Visual Studio, TFS, GIT, Visio, LucidChart, NewRelic}
    \cvline{\textbf{Framework / Server}}{React, Bootstrap, AngularJS, .NET, IIS, AWS, Pivotal}
    \cvline{\textbf{Languages}}{JS, HTML/CSS, SQL, Python, C}
    \cvline{\textbf{Databases}}{MSSQL, MYSQL}

    %\section{Interests/Personal Projects}
    %\cvlistdoubleitem{Embedded Systems}{IoT}
    %\cvlistdoubleitem{Woodworking}{3D Printing}

    \end{document}
    